---
title: "MRI Basic"
---

```{r setup, include=FALSE}
library(here)
library(dplyr)
library(tibble)
library(gt)
```

## Intensity Pattern

### Mono

Compare intensity to grey matter.

-   **Hypo T1:** fluid (chronic lesion)

-   **Hyper T1:** 
    -   Fat (except `T1FS`)
    -   Protein (depend on content)
    -   Blood (early & late subacute)
    -   Paramagnetic, Melanin

-   **Hyper T2:** fluid (CSF) > fat   


### Combined


-   **Hypo T1 & T2:** Air, Flow void (high-flow vessel), Calcification

-   **Iso T1 & T2:** Muscle




-   **Hypo T1 + Hyper T2:** fluid





## Blood Signal

![MRI Signal of Aging Blood [@bradleyMRAppearanceHemorrhage1993] and [blog post](https://limpeter-mriblog.blogspot.com/2009/12/mr-signal-intensity-of-aging-blood.html)](../img/neuro/MRI-signal-blood.png){#fig-mri-sig-blood width="60%"}


```{r txt_mri}
txt_mri <- list(
    iso = "**I**sointense",
    bright = "**B**right",
    dark = "**D**ark"
)
```

```{r mri_blood_sig_gt}
mri_blood_sig_gt <- tibble::tribble(
   ~Hemorrhage, ~Time, ~T1, ~T2,
    "Hyperacute", "\\< 12 hr", txt_mri$iso, txt_mri$bright,
    "Acute", "12 hr - 2 days",  txt_mri$iso, txt_mri$dark,
    "Early subacute", "2 - 7 days", txt_mri$bright, txt_mri$dark,
    "Late subacute", "1 wks - 2 mos", txt_mri$bright, txt_mri$bright,
    "Chronic", "\\> 2 mos", txt_mri$dark, txt_mri$dark
)  %>% 
  gt(rowname_col = "Hemorrhage") %>% 
  fmt_markdown(columns = everything()) %>% 
  # Style: Stub
  tab_style(
    style = cell_text(weight = "bold" , size = 15),
    locations = cells_stub()
  ) %>% 
  # Style: Column Labels
  tab_style(
    style = list(cell_text(weight = "bold", size = 15), 
                 cell_fill(color = "lightgrey")),
    locations = cells_column_labels()
  )

mri_blood_sig_gt
```
